Topological Eulerian Synthesis of Slow Motion Periodic Videos

### 2018-02-05 Paper/paper.tex
small edits to 2.4

Given the phase estimates $\phi_i$, we can now synthesize the final slow motion template by lining up the $N$ sliding windows $SW_{d}[\mb{X}(i)]$ by $\phi$.  For a template with $M$ frames, we choose a set of $M$ equally spaced angles $\theta_1, \theta_2, ..., \theta_M$ around the circle at which to sample the template.  Let $\Phi_i$ be the unwrapped phase of $\phi_i$.  Based on this, we esimate the number of periods $X(t)$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.  Assuming $k$ is correct and that $\phi_i$ has a constant slope over $i$, there is a phase gap of $2 \pi k/N$ between adjacent stacked frames in each sliding window.  Thus, $SW_{d}[\mb{X}(i)]$ spans the interval $[\phi_i, \phi_i + 2\pi k d/N (\text{mod} 2 \pi)]$.  A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames in each window, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.  We then take a pixel-wise median of all such interpolated frames, and we let that be the final frame at position $j$ in the template.  In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ``ghosting'' artifacts in linear interpolation \cite{meyer2015phase}.  We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{RobustnessTests.pdf}
\caption{Robustness tests.}
\label{fig:RobustnessTests}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{RobustnessTestsNoSW.pdf}
\caption{Robustness tests without sliding window.}
\label{fig:RobustnessTestsNoSW}
\end{figure}

We first experimentally quantify the accuracy of our circular coordinate inference, since we cannot hope to get a good slow motion template unless our circular coordinates are accurate.  We generate 3 different 600 frame synthetic periodic videos for which we know the ground truth circular coordinates, using software from \cite{jacobson2012fast}.  We vary the number of cycles that the videos undergo between 3, 5, 10, 15, 20, 25, 30, 40, and 50, and we also vary the ``shake'' of the video (width of a motion blur kernel) from 0, $20 \times 20$, $40 \times 40$, and $80 \times 80$, to assess the effect of drift.  We also compare different fractions $\kappa$ of mutual nearest neighbors to tune the threshold at which the unweighted Laplacian is built to TDA for aututuning the scale.  Figure~\ref{fig:RobustnessTests} shows the average angular error in degrees for our entire pipeline, and Figure~\ref{fig:RobustnessTests}.  The errors are overall quite low for moderate shake with a sliding window, though they increase as more shake is introduced.  Without a sliding window, the only video that performs reasonably well is the ``crowd'' videom, though the errors increase with shake much more rapidly than with the sliding window, supporting the ``time regularization'' properties of the sliding window.

>>>>

Given the phase estimates $\phi_i$, we can now synthesize the final slow motion template by lining up the $N$ sliding windows $SW_{d}[\mb{X}(i)]$ by $\phi$.  For a template with $M$ frames, we choose a set of $M$ equally spaced angles $\theta_1, \theta_2, ..., \theta_M$ around the circle at which to sample the template.  Let $\Phi_i$ be the unwrapped phase of $\phi_i$.  Based on this, we esimate the number of periods $X(t)$ goes through as $k = (N \times \max_i(\Phi_i) / (2 \pi (N-d+1)))$.  Assuming $k$ is correct and that $\phi_i$ has a constant slope over $i$, there is a phase gap of $2 \pi k/N$ between adjacent stacked frames in each sliding window.  Thus, $SW_{d}[\mb{X}(i)]$ spans the interval $[\phi_i, \phi_i + 2\pi k d/N (\text{mod} 2 \pi)]$.  A given $\theta_j$ will potentially be contained in the intervals for many different windows, though it is unlikely to coincide exactly with any of the frames in each window, so we use linear interpolation to fill in a frame corresponding to $\theta_j$ in each window overlapping it.  The frame at angle $\phi_j$ is taken as the median of all interpolated frames.  In practice, for videos which go through many periods, the gap between stacked frames within a window may be large, leading to ghosting artifacts in linear interpolation \cite{meyer2015phase}.  We thus add an additional user-defined parameter ``F'' which only includes linearly interpolated frames in the median if the frame to interpolate is at most $F$ frames away from an existing frame in the window. % MSB: I do not understand this last sentence..

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{RobustnessTestsShake.pdf}
\caption{Robustness tests.}
\label{fig:RobustnessTestsShake}
\end{figure}

We first experimentally quantify the accuracy of our circular coordinate inference, since we cannot hope to get a good slow motion template unless our circular coordinates are accurate.  We generate 3 different 600 frame synthetic periodic videos for which we know the ground truth circular coordinates, using software from \cite{jacobson2012fast}.  We vary the number of cycles that the videos undergo between 3, 5, 10, 15, 20, 25, 30, 40, and 50, and we also vary the ``shake'' of the video (width of a motion blur kernel) from 0, $20 \times 20$, $40 \times 40$, and $80 \times 80$, to assess the effect of drift.  We also compare different fractions $\kappa$ of mutual nearest neighbors to tune the threshold at which the unweighted Laplacian is built to TDA for aututuning the scale.  Figure~\ref{fig:RobustnessTestsShake} shows the average angular error in degrees for our entire pipeline under different amounts of shake.  The errors are overall quite low for moderate shake with a sliding window, though they increase as more shake is introduced.  Without a sliding window, the only video that performs reasonably well is the ``crowd'' videom, though the errors increase with shake much more rapidly than with the sliding window, supporting the ``time regularization'' properties of the sliding window.
